\section{Introduction}
Quality data preprocessing is an important prerequisite to creating accurate machine learning models. It solves a wide range of problems, from missing data and data inconsistency to required anonymization. In our project we have decided to focus primarily on one aspect of it, that is, \textbf{feature selection}. \\

However, the main problem that can be solved by feature selection for multiple regression models (and will be addressed specifically in our project) is \textbf{multicollinearity}. Multicollinearity is an effect when multiple explanatory variables that are believed to me independent from each other, are in fact, closely interrelated. This can have damaging effects on the accuracy of prediction models, as even a small change in data will lead to unpredictable results. Ideally, feature selections would find such relationships and purge the dataset from them, our model aims to do so as well.\\
\section{Related Work}




\section{Methodology}
\subsection{Linear model selection}
We have designed and trained two separate tools for this task. Each is concerned with one of the two main branches of Supervised Learning problems (Classification and Regression).
The model concerned with Regression problems was a choice among many models that were trained and tested on the dataset that was manually built by our team from the world data bank (Ransac and Linear Regression, Decision Tree, Random Forest, etc…). These models were fine-tuned using Cross-Validation Method in order to be customized so that they generate the most accurate predictions. After that, the model with the lowest mean squared error was chosen (Ransac Regressor).\\

The model concerned with classification was determined in a similar manner. We built and trained several models (KNN, Logistic Regression, Decision Tree, Random Forest, etc...) using a dataset generated specifically for this purpose. Then, the models were similarly tuned to give highly valuable insights into our dataset and the model with the highest accuracy was chosen.